Co-moving stars in \textsl{Gaia DR1}:\\ An abundance of very wide separation co-moving pairs

### 2017-04-18 paper/table_meta.tex
put in new columns and make schema standalone

\begin{table}[htb]
\centering
\caption{Candidate co-moving pairs catalog description} \label{tab:table_meta}
\begin{tabular}{l|l|l}
\hline\hline
Column Name    & Unit & Description                         \\
\hline
\multicolumn{3}{c}{Table: Star (10,606 rows)}                                         \\
\hline
row id         &      & Zero-based row index                      \\
TGAS source id &      & Unique source id from \tgas               \\
RA             & deg  & Right ascension from \tgas                \\
DEC            & deg  & Declination from \tgas                    \\
parallax       & mas  & Unique source id from \tgas               \\
distance       & pc   & Unique source id from \tgas               \\
$G$            & mag  & \gaia\ $G$-band magnitudes                \\
$J$            & mag  & \tmass\ $J$-band magnitudes               \\
RAVE OBS ID    &      & Unique id of the \rave\ match             \\
RV             & \kms & Radial velocity from \rave\               \\
eRV            & \kms & Uncertainty of radial velocity from \rave \\
group id       &      & Id of the group this star belongs to      \\
\hline
\multicolumn{3}{c}{Table: Pair (13,058 rows)}                                            \\
\hline
star 1                           &        & Index of star 1 in the star table   \\
star 2                           &        & Index of star 2 in the star table   \\
angsep                           & arcmin & Angular separation                  \\
separation                       & pc     & Physical separation                 \\
$\ln\mathcal{L}_1/\mathcal{L}_2$ &        & Likelihood ratio                    \\
group id                         &        & Id of the group the pair belongs to \\
\hline
\multicolumn{3}{c}{Table: Group (4,555 rows)}                                         \\
\hline
id            &        & Unique group id                     \\
size          &        & Number of stars in a group          \\
mean RA       &  deg   & Mean right ascension of members     \\
mean DEC      &  deg   & Mean declination of members     \\
mean distance &  pc    & Mean distance of members     \\
\hline\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[htb]
\centering
\caption{Candidate co-moving pairs catalog description} \label{tab:table_meta}
\begin{tabular}{l|l|l}
\hline\hline
Column Name    & Unit & Description                         \\
\hline
\multicolumn{3}{c}{Table: Star (10,606 rows)}                                         \\
\hline
row id         &      & Zero-based row index                      \\
TGAS source id &      & Unique source id from \tgas               \\
Name           &      & \project{Hipparcos} or \project{Tycho-2} identifier \\
RA             & deg  & Right ascension from \tgas                \\
DEC            & deg  & Declination from \tgas                    \\
parallax       & mas  & Unique source id from \tgas               \\
distance       & pc   & Unique source id from \tgas               \\
$G$            & mag  & \gaia\ $G$-band magnitudes                \\
$J$            & mag  & \tmass\ $J$-band magnitudes               \\
RAVE OBS ID    &      & Unique id of the \rave\ match             \\
RV             & \kms & Radial velocity from \rave\               \\
eRV            & \kms & Uncertainty of radial velocity from \rave \\
group id       &      & Id of the group this star belongs to      \\
group size     &      & Size of the group this star belongs to    \\
\hline
\multicolumn{3}{c}{Table: Pair (13,058 rows)}                                            \\
\hline
star 1                           &        & Index of star 1 in the star table   \\
star 2                           &        & Index of star 2 in the star table   \\
angsep                           & arcmin & Angular separation                  \\
separation                       & pc     & Physical separation                 \\
$\ln\mathcal{L}_1/\mathcal{L}_2$ &        & Likelihood ratio                    \\
group id                         &        & Id of the group the pair belongs to \\
group size                       &        & Size of the group the pair belongs to \\
\hline
\multicolumn{3}{c}{Table: Group (4,555 rows)}                                         \\
\hline
id            &        & Unique group id                     \\
size          &        & Number of stars in a group          \\
mean RA       &  deg   & Mean right ascension of members     \\
mean DEC      &  deg   & Mean declination of members     \\
mean distance &  pc    & Mean distance of members     \\
\hline\hline
\end{tabular}
\end{table}
